\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}
\usepackage{amssymb}

% Custom command for rubric items
\newcommand{\rubricitem}[2]{\textbf{#1:} #2}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{1.2em}{0.6em}

\begin{document}

\begin{center}
    {\LARGE\bfseries \textit{Lasers and Optomechanics} --- PHY 400/800 }\\[0.5em]
    {\normalsize Final Project Peer Assessment}\\[0.2em]
\end{center}

\vspace{1em}

\noindent\textbf{Name:} \\[1em]
\noindent\textbf{Presenter:} 

\vspace{1.5em}

% -------------------------------------------------------
\section*{1.\quad Motivation}

\begin{itemize}[leftmargin=1.5em, itemsep=0.4em]
    \item[$\square$] \rubricitem{Great}{I understand why this topic is important to the scientific community.}
    \item[$\square$] \rubricitem{Good}{I have an idea about why this topic is important.}
    \item[$\square$] \rubricitem{Ok}{I can understand why some people find this topic interesting.}
    \item[$\square$] \rubricitem{Needs work}{Motivation is missing for this topic.}
\end{itemize}

% -------------------------------------------------------
\section*{2.\quad Scientific Rigor and Depth of Knowledge}

\begin{itemize}[leftmargin=1.5em, itemsep=0.4em]
    \item[$\square$] \rubricitem{Great}{The technical details are well-explained and the group demonstrates full knowledge by answering all class questions with explanations and elaboration.}
    \item[$\square$] \rubricitem{Good}{There are some technical details that are well-explained, and the group is at ease with expected answers to most questions, but fails to elaborate.}
    \item[$\square$] \rubricitem{Ok}{The technical details are present but not cohesive; the group is uncomfortable with information and is able to answer only rudimentary questions.}
    \item[$\square$] \rubricitem{Needs work}{Technical details are absent, the group does not have a grasp of information; group cannot answer questions about the subject.}
\end{itemize}

% -------------------------------------------------------
\section*{3.\quad Graphics and Mathematics}

\begin{itemize}[leftmargin=1.5em, itemsep=0.4em]
    \item[$\square$] \rubricitem{Great}{The group's graphics/math explain and reinforce the presentation.}
    \item[$\square$] \rubricitem{Good}{The group's graphics/math relate to the content of the presentation.}
    \item[$\square$] \rubricitem{Ok}{The group occasionally uses graphics/math that rarely support the presentation.}
    \item[$\square$] \rubricitem{Needs work}{The group uses superfluous graphics/math or no graphics/math.}
\end{itemize}


% -------------------------------------------------------
\section*{4.\quad Presentation \& Elocution}

\begin{itemize}[leftmargin=1.5em, itemsep=0.4em]
    \item[$\square$] \rubricitem{Great}{Presenter(s) maintains eye contact with audience, seldom returning to notes, and spoke clearly.}
    \item[$\square$] \rubricitem{Good}{Presenter(s) maintains eye contact most of the time but frequently returns to notes, and spoke clearly most of the time.}
    \item[$\square$] \rubricitem{Ok}{Presenter(s) occasionally make eye contact, but still mostly reads report; presenters hard to hear or unclear elocution.}
    \item[$\square$] \rubricitem{Needs work}{Presenter(s) read all of presentation with no eye contact; presenters mumble and cannot be understood.}
\end{itemize}


% -------------------------------------------------------
\section*{5.\quad References}

\begin{itemize}[leftmargin=1.5em, itemsep=0.4em]
    \item[$\square$] \rubricitem{Great}{References are cited in the presentation and are excellent reviews of the topic.}
    \item[$\square$] \rubricitem{Good}{References are present and help elucidate the topic.}
    \item[$\square$] \rubricitem{Ok}{References are too few, or are not very relevant to the topic.}
    \item[$\square$] \rubricitem{Needs work}{References are missing, are not relevant, or are from weak sources.}
\end{itemize}

% -------------------------------------------------------
\section*{6.\quad The Most Interesting Thing I Learned}

\vspace{5cm}

% -------------------------------------------------------
\section*{7.\quad I Would Like to Learn More About}


\vspace{5cm}

\end{document}