\documentclass[10pt, letterpaper]{article}

\usepackage[top=0.65in, bottom=0.65in, left=0.75in, right=0.75in]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{makecell}
\usepackage{parskip}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\definecolor{headerblue}{RGB}{31, 73, 125}
\definecolor{rowshade}{RGB}{220, 230, 242}
\definecolor{lightgray}{RGB}{245, 245, 245}

\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\setlength{\parskip}{0pt}

\begin{document}

% ============================================================
%  PAGE 1 — Rubric table
% ============================================================
\begin{center}
  {\large\bfseries\color{headerblue} In-Class Science Presentation Rubric}\\[4pt]
  {\small Presenter: \underline{\hspace{10cm}} \;
   Date: \underline{\hspace{2.5cm}}}\\[2pt]
  {\small Topic: \underline{\hspace{12.8cm}}}
\end{center}

\vspace{3pt}
{\small\textbf{Instructions:} Circle or highlight the score that best describes the presentation in each category.
Record earned points in the score summary on page~2. Maximum total: \textbf{100 points}.}

\vspace{6pt}

\renewcommand{\arraystretch}{1.35}
\setlength{\tabcolsep}{4pt}
\footnotesize

\noindent
\begin{tabularx}{\textwidth}{L{2.6cm} C{0.85cm} X X X X}

\rowcolor{headerblue}
\makecell[tl]{\textcolor{white}{\textbf{Category}}}
  & \textcolor{white}{\textbf{Score}}
  & \makecell[tl]{\textcolor{white}{\textbf{Excellent}}}
  & \makecell[tl]{\textcolor{white}{\textbf{Proficient}}}
  & \makecell[tl]{\textcolor{white}{\textbf{Developing}}}
  & \makecell[tl]{\textcolor{white}{\textbf{Beginning}}}\\
\toprule

\rowcolor{lightgray}
\makecell[tl]{\textbf{1. Scientific}\\\textbf{Rigor}\\(25 pts)}
  & \makecell[tc]{$\bigcirc$\,25\\[3pt]$\bigcirc$\,20\\[3pt]$\bigcirc$\,15\\[3pt]$\bigcirc$\,10\\[3pt]$\bigcirc$\,5\\[3pt]$\bigcirc$\,0}
  & All claims are precise and scientifically accurate. Assumptions are clearly stated and justified. Quantitative analysis is included where appropriate, and limitations are explicitly acknowledged.
  & Most claims are accurate with only minor errors. Some quantitative support is provided. A few assumptions go unstated and limitations are only briefly mentioned.
  & Several claims are vague or inaccurate. Quantitative analysis is limited. Assumptions and limitations of the work are not discussed.
  & Claims are largely inaccurate or unsupported. No quantitative analysis. No discussion of assumptions, uncertainties, or limitations.\\
\midrule

\rowcolor{rowshade}
\makecell[tl]{\textbf{2. Motivation}\\\textbf{\& Context}\\(25 pts)}
  & \makecell[tc]{$\bigcirc$\,25\\[3pt]$\bigcirc$\,20\\[3pt]$\bigcirc$\,15\\[3pt]$\bigcirc$\,10\\[3pt]$\bigcirc$\,5\\[3pt]$\bigcirc$\,0}
  & A compelling case is made for why the topic matters. Strong connections to broader scientific or societal questions are drawn. The audience is clearly engaged and oriented from the outset.
  & The importance of the topic is stated but not deeply argued. Context is provided at a surface level. The opening is generally engaging but lacks depth.
  & Motivation is vague or unconvincing. Little effort is made to connect the topic to broader questions. The audience is not clearly oriented to the subject.
  & No motivation is provided. The topic is introduced without context. The audience is left unclear on the significance or relevance of the work.\\
\midrule

\rowcolor{lightgray}
\makecell[tl]{\textbf{3. Research}\\\textbf{\& References}\\(25 pts)}
  & \makecell[tc]{$\bigcirc$\,25\\[3pt]$\bigcirc$\,20\\[3pt]$\bigcirc$\,15\\[3pt]$\bigcirc$\,10\\[3pt]$\bigcirc$\,5\\[3pt]$\bigcirc$\,0}
  & Draws on peer-reviewed primary literature; sources are current and authoritative. All references are properly and consistently cited. Evidence is engaged critically and placed in appropriate context.
  & Research is based mostly on primary sources; references cited with minor inconsistencies. Evidence is used appropriately and supports the main claims.
  & A mix of primary and popular sources is used; some claims lack citations. Evidence is occasionally misinterpreted or used out of context.
  & Research relies mainly on non-scholarly sources; few or no citations provided. Evidence is poorly used or misrepresented.\\
\midrule

\rowcolor{rowshade}
\makecell[tl]{\textbf{4. Presentation}\\\textbf{Style}\\(25 pts)}
  & \makecell[tc]{$\bigcirc$\,25\\[3pt]$\bigcirc$\,20\\[3pt]$\bigcirc$\,15\\[3pt]$\bigcirc$\,10\\[3pt]$\bigcirc$\,5\\[3pt]$\bigcirc$\,0}
  & Delivery is clear, confident, and well-paced. Visuals are effective, uncluttered, and enhance understanding. Timing is well managed and audience questions are answered knowledgeably.
  & Delivery is generally clear with minor hesitations. Visuals support the content adequately. The presentation is mostly on time and most questions are handled well.
  & Delivery is unclear at times; visuals are cluttered or insufficient. The presentation runs over or under time and some questions are not addressed adequately.
  & Delivery is inaudible or very difficult to follow. Visuals are absent or confusing. Timing is poor and the presenter is unable to address audience questions.\\
\bottomrule
\end{tabularx}

\newpage
\normalsize

% ============================================================
%  PAGE 2 — Score Summary + Feedback
% ============================================================
\begin{center}
  {\large\bfseries\color{headerblue} Score Summary \& Feedback}\\[4pt]
  {\small Presenter: \underline{\hspace{6cm}} \quad Topic: \underline{\hspace{6cm}}}
\end{center}

\vspace{8pt}
\renewcommand{\arraystretch}{1.6}
\setlength{\tabcolsep}{5pt}
\noindent
\begin{tabularx}{\textwidth}{L{9cm} C{2cm} X}
\rowcolor{headerblue}
  \textcolor{white}{\textbf{Category}} &
  \textcolor{white}{\textbf{Max}} &
  \textcolor{white}{\textbf{Points Earned}}\\
\midrule
\rowcolor{lightgray}  \textbf{1.}\ Scientific Rigor        & 25  & \\
\rowcolor{rowshade}   \textbf{2.}\ Motivation \& Context   & 25  & \\
\rowcolor{lightgray}  \textbf{3.}\ Research \& References  & 25  & \\
\rowcolor{rowshade}   \textbf{4.}\ Presentation Style      & 25  & \\
\midrule
\rowcolor{headerblue} \textcolor{white}{\textbf{Total}} & \textcolor{white}{\textbf{100}} & \\
\end{tabularx}

\vspace{12pt}
\noindent{\color{headerblue}\textbf{\large Notes}}
\vspace{4pt}

\noindent\colorbox{lightgray}{\makebox[\dimexpr\textwidth-2\fboxsep]{\textbf{\strut 1. Scientific Rigor}}}\\[20pt]


\vspace{8pt}
\noindent\colorbox{rowshade}{\makebox[\dimexpr\textwidth-2\fboxsep]{\textbf{\strut 2. Motivation \& Context}}}\\[20pt]


\vspace{8pt}
\noindent\colorbox{lightgray}{\makebox[\dimexpr\textwidth-2\fboxsep]{\textbf{\strut 3. Research \& References}}}\\[20pt]


\vspace{8pt}
\noindent\colorbox{rowshade}{\makebox[\dimexpr\textwidth-2\fboxsep]{\textbf{\strut 4. Presentation Style}}}\\[20pt]


\vspace{12pt}
\noindent{\color{headerblue}\textbf{\large Overall Feedback}}
\vspace{4pt}

\noindent\textbf{Strengths:}\\[4pt]
\\[20pt]
\vspace{8pt}
\noindent\textbf{Areas for Improvement:}\\[4pt]
\\[20pt]

\vspace{14pt}
\noindent

\textbf{Final Grade:} \underline{\hspace{3cm}}\\[4pt]
\textbf{Date:} \underline{\hspace{3cm}}

\end{document}